\begin{abstract}
The development of cyber-physical systems (CPS) is a challenge due to the heterogeneity between different subsystems. To assist the development process, co-simulation can be used, where models of constituents of a CPS are coupled to jointly simulate the behavior of full system. However, a trustworthy result of the co-simulation is only obtained if all of the simulation units are initialized in the correct order. In this work, we consider co-simulation where the simulation units are described as Functional Mock-up Units (FMU). The Functional Mock-up Interface specification specifies constraints to the initialization of variables in the scope of a single FMU. However, it does not consider the initialization of interconnected variables between instances of FMUs. Such interconnected variables place particular constraints on the initialization order of the FMUs.\\
The approach taken to calculate a correct initialization order is based on predicates from the specification and the topological ordering of both internal connections and interconnected variables. Circular dependencies between FMU variables are dismissed. %This approach has been compared to other already existing approaches for FMI initialization. 
The approach has been realized as a plugin for the open-source INTO-CPS Maestro 2 Co-simulation tool. It has been tested for various scenarios and compared to an existing \textit{Initializer} that has been validated through academic and industrial application.

\keywords{Co-simulation \and Initialization \and Topological ordering \and FMI}
\end{abstract}

%The correct initialization of a co-simulation depends not only on the value being assigned to each port but also the order in which the ports are initialized.



